A Formal Model of Checked C

### 2022-11-22 sandp23/background.tex
Make file modifications

@@

% 
\mz{The example itself is a bit confusing.
  %
  There are a few simplifications can be made here:
  % 
  (1) introduce a macro: \code{#define nt_ptr nt_array_ptr} to make the example
  less verbose;
  % 
  (2) split untangle BAD and GOOD code into 2 fragments, listed side-by-side.
  %
  (3) use more descriptive function name instead of \code{f}, \code{g}
}
%

>>>>

\section{Background}
\subsection{Program Partitioning}
\label{subsec:background:programpart}

@@

% 
%\mz{The example itself is a bit confusing.
  %
%  There are a few simplifications can be made here:
  % 
%  (1) introduce a macro: \code{#define nt_ptr nt_array_ptr} to make the example
%  less verbose;
  % 
%  (2) split untangle BAD and GOOD code into 2 fragments, listed side-by-side.
  %
%  (3) use more descriptive function name instead of \code{f}, \code{g}
%}
%
